Supplementary Material for Food-web complexity alters the fitness landscape of an insect herbivore

### 2018-05-02 supp_mat_complexity_selection.Rmd

```{r FUNCTIONS}
gam.plot <- function(gam.model, ...) {
  plot(gam.model, seWithMean = T, shift = mean(predict(gam.model)), trans = function(x) {exp(x)/(1+exp(x))}, ...)
}

@@

## CONTROL PLANTS ----
gam_red.control <- gam(gall_survival ~
                         s(c.Gall_Height_mm) + 
                         s(c.gall_individuals, k=9) +
                         s(c.Density_per_100_shoots),
                       data = control_df, family = binomial(link = "logit"))
summary(gam_red.control)

@@

## TREATMENT PLANTS ----
gam_red.treatment <- gam(gall_survival ~
                         s(c.Gall_Height_mm) + 
                         s(c.gall_individuals, k=9) +
                         s(c.Density_per_100_shoots),
                       data = treatment_df, family = binomial(link = "logit"))
summary(gam_red.treatment)

@@

@@

```{r}
size_models <- gall_selection.df %>%
  group_by(Treatment.focus, Genotype) %>%
  do(model = lm(gall_survival ~ Gall_Height_mm, data = .)) %>%
  tidy(model) %>%
  ungroup()

size_models %>%
  ggplot(., aes(x=Genotype, y=estimate, fill=Treatment.focus)) +
  geom_bar(stat="identity", position = "dodge") +
  geom_errorbar(aes(ymax = estimate + std.error, ymin = estimate - std.error), #, color=Treatment.focus
                width = 0.5, position = position_dodge(width = 0.8)) +
  facet_wrap(~term, scales = "free_y")
```

```{r}
size.grad_models <- gall_selection.df %>%
  group_by(Treatment.focus, Genotype) %>%
  do(model = lm(gall_survival/mean(gall_survival) ~ I(Gall_Height_mm - mean(Gall_Height_mm)), data = .)) %>%
  tidy(model) %>%
  ungroup()
size.grad_models

size.grad_models %>%
  filter(term != "(Intercept)") %>%
  ggplot(., aes(x=Genotype, y=estimate, fill=Treatment.focus)) +
  geom_bar(stat="identity", position = "dodge") +
  geom_errorbar(aes(ymax = estimate + std.error, ymin = estimate - std.error), #, color=Treatment.focus
                width = 0.5, position = position_dodge(width = 0.8))

size.grad_models %>%
  filter(term != "(Intercept)") %>%
  ggplot(., aes(x=Treatment.focus, y=estimate, fill=Genotype, group=Genotype)) +
  geom_line() +
  geom_point(shape=21, position = "dodge", size=4) +
  geom_hline(yintercept=0, linetype="dotted")

summary(lm(estimate ~ Treatment.focus, data = filter(size.grad_models, term != "(Intercept)")))
```

>>>>

```{r FUNCTIONS}
gamm.model <- function(formula, data) {
  gamm4(formula, data, 
        random = ~(1|Genotype/Plant_Position/Gall_Number),
        family = binomial(link = logit))
}

gam.plot <- function(gam.model, ...) {
  plot(gam.model, seWithMean = T, shift = mean(predict(gam.model)), trans = function(x) {exp(x)/(1+exp(x))}, ...)
}

@@

## CONTROL PLANTS ----

## Gall Height
gam_red.control_size <- gam(gall_survival ~
                             s(c.Gall_Height_mm) + 
                             c.gall_individuals +
                             c.Density_per_100_shoots,
                           data = control_df, family = binomial(link = "logit"))
summary(gam_red.control)

@@

## Gall individuals
control_df_gall.level <- control_df %>%
  group_by(Treatment.focus, Plant_Position, Gall_Number) %>%
  summarise(gall_survival_mean = mean(gall_survival),
            gall_individuals = mean(gall_individuals),                 # note that there is no variance, it is the actual value
            Gall_Height_mm_mean = mean(Gall_Height_mm),
            Density_per_100_shoots = mean(Density_per_100_shoots)) %>% # remember that this is pseudo-replicated at the gall-level
  ungroup() %>%
  mutate(c.Gall_Height_mm_mean = Gall_Height_mm_mean - mean(Gall_Height_mm_mean),
         c.gall_individuals = gall_individuals - mean(gall_individuals),
         c.Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots)) # why is this giving zero values?

gam_red.control_indiv <- gam(gall_survival_mean ~
                              c.Gall_Height_mm_mean + 
                              s(c.gall_individuals, k=9) +
                              c.Density_per_100_shoots,
                             data = control_df_gall.level, family = binomial(link = "logit")) # we didn't include weights because this would be correlated with the number of individuals per gall
summary(gam_red.control_indiv)

gam.plot(gam_red.control_indiv)
gam.plot(gamm_red.control$gam)

## Gall density
control_df_plant.level <- control_df_gall.level %>%
  group_by(Treatment.focus, Plant_Position) %>%
  summarise(gall_survival_mean = mean(gall_survival_mean),
            gall_sample_size = n(),
            gall_individuals_mean = mean(gall_individuals),                 
            Gall_Height_mm_mean = mean(Gall_Height_mm_mean),
            Density_per_100_shoots = mean(Density_per_100_shoots)) %>%                # note that there is no variance, it is the actual value
  ungroup() %>%
  mutate(c.Gall_Height_mm_mean = Gall_Height_mm_mean - mean(Gall_Height_mm_mean),
         c.gall_individuals_mean = gall_individuals_mean - mean(gall_individuals_mean),
         c.Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots)) # why is this giving zero values?

gam_red.control_density <- gam(gall_survival_mean ~
                                c.Gall_Height_mm_mean + 
                                c.gall_individuals_mean +
                                s(c.Density_per_100_shoots, k=3),   # do I adjust k to be consistent with mixed-effects model?
                             data = control_df_plant.level, family = binomial(link = "logit"), weights = gall_sample_size) # weighting appears to alter the results...
summary(gam_red.control_density)

gam.plot(gam_red.control_density)
gam.plot(gamm_red.control$gam)

## TREATMENT PLANTS ----

## Gall Height
gam_red.treatment_size <- gam(gall_survival ~
                         s(c.Gall_Height_mm) + 
                         c.gall_individuals +
                         c.Density_per_100_shoots,
                       data = treatment_df, family = binomial(link = "logit"))
summary(gam_red.treatment)

@@

## Gall individuals
treatment_df_gall.level <- treatment_df %>%
  group_by(Treatment.focus, Plant_Position, Gall_Number) %>%
  summarise(gall_survival_mean = mean(gall_survival),
            gall_individuals = mean(gall_individuals),                 # note that there is no variance, it is the actual value
            Gall_Height_mm_mean = mean(Gall_Height_mm),
            Density_per_100_shoots = mean(Density_per_100_shoots)) %>% # remember that this is pseudo-replicated at the gall-level
  ungroup() %>%
  mutate(c.Gall_Height_mm_mean = Gall_Height_mm_mean - mean(Gall_Height_mm_mean),
         c.gall_individuals = gall_individuals - mean(gall_individuals),
         c.Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots)) # why is this giving zero values?

gam_red.treatment_indiv <- gam(gall_survival_mean ~
                              c.Gall_Height_mm_mean + 
                              s(c.gall_individuals, k=9) +
                              c.Density_per_100_shoots,
                             data = treatment_df_gall.level, family = binomial(link = "logit"))
summary(gam_red.treatment_indiv)

gam.plot(gam_red.treatment_indiv)
gam.plot(gamm_red.treatment$gam)

## Gall density
treatment_df_plant.level <- treatment_df_gall.level %>%
  group_by(Treatment.focus, Plant_Position) %>%
  summarise(gall_survival_mean = mean(gall_survival_mean),
            gall_sample_size = n(),
            gall_individuals_mean = mean(gall_individuals),                 
            Gall_Height_mm_mean = mean(Gall_Height_mm_mean),
            Density_per_100_shoots = mean(Density_per_100_shoots)) %>%                # note that there is no variance, it is the actual value
  ungroup() %>%
  mutate(c.Gall_Height_mm_mean = Gall_Height_mm_mean - mean(Gall_Height_mm_mean),
         c.gall_individuals_mean = gall_individuals_mean - mean(gall_individuals_mean),
         c.Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots)) # why is this giving zero values?

gam_red.treatment_density <- gam(gall_survival_mean ~
                                c.Gall_Height_mm_mean + 
                                c.gall_individuals_mean +
                                s(c.Density_per_100_shoots),
                             data = treatment_df_plant.level, family = binomial(link = "logit"), weights = gall_sample_size) # weighting appears to alter the results...
summary(gam_red.treatment_density)

gam.plot(gam_red.treatment_density)
gam.plot(gamm_red.treatment$gam)

@@
